Pillar 1 - Sequential Pattern Mining

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
minor update

### Transcript with Preceding courses per student
```{r}

@@

#
# courses taken so far and not taken so far
d_cumulative_transcript <- d_transactions$taken_PF_HL %>%

>>>>

### Transcript with Preceding courses per student
```{r d_transcript_cum}

@@

#
# courses taken so far and not taken so far
d_transcript_cum <- d_transactions$taken_PF_HL %>%
